% -----------------------------------------------------------------------
% Question 3.1
% -----------------------------------------------------------------------

\begin{question}{3.1}
Explain the idea of K-fold cross-validation and why it is useful. How the choice of K (in the cross-validation) impacts the bias and the variance of the scores obtained on the different folds? Choose and justify the number of folds you consider in this project. 
\end{question}

\begin{answer}{12} 
    Your answer to question 2.1 in this box.\\
\end{answer}



% -----------------------------------------------------------------------
% Question 3.2
% -----------------------------------------------------------------------

\begin{question}{3.2}
Explain your methodology of model evaluation. More precisely, explain which hyperparameters you tune and the values you test for each of them. Next, provide the best hyperparameters configuration for each of the three models as well as their CV F1 score. 
\end{question}

\begin{answer}{14.5} 
    Your answer to question 3.2 in this box.\\
\end{answer}



% -----------------------------------------------------------------------
% Question 3.3
% -----------------------------------------------------------------------

\begin{question}{3.3}
Based on your answers to previous questions, select a final model that you will keep as classifier. Justify. 
\end{question}

\begin{answer}{2} 
    Your answer to question 3.3 in this box.\\
\end{answer}


% -----------------------------------------------------------------------
% Question 3.4
% -----------------------------------------------------------------------

\begin{question}{3.4}
Plot the precision-recall curve for the three methods, one figure for each class. What happens to the precision and recall when the threshold tends to 0? And when it tends to 1? Explain and, if possible, establish a link with Question 2.1.
For each class, for each method: what threshold would you use?  
\end{question}

\begin{answer}{18} 
    Your answer to question 3.4 in this box.\\
\end{answer}
